Approximation as Differentiation

### 2025-07-10 main/language.tex
Introduce signatures in syntax.

The language includes base types $\rho$ drawn from a set $\PrimTy$, along with standard type formers for sums,
products, functions and lists, and an additional lifting type constructor $\tyLift$ to allow approximation
points to be added explicitly, as discussed in \secref{models-of-total-gps}. Terms include variables, the
usual introduction and elimination forms, a monadic return and bind for lifted terms, and primitive operations
$\phi$ of arity $n$ drawn from a family of sets $\PrimOp^\rho_{\rho_1,\ldots,\rho_n}$.

The language is intentionally minimal: it excludes general recursion, and general inductive or coinductive
types, which will consider in future work (\secref{conclusion}). Typing judgments for terms are standard and
shown in \figref{typing}, with the usual rules for products, sums, functions, lists and lifting.

@@

>>>>

The language is parameterised by a signature $\Sigma = (\PrimTy, \PrimOp)$ consisting of a set $\PrimTy$ of
base types $\rho$ and a family of sets $\PrimOp^\rho_{\rho_1,\ldots,\rho_n}$ of primitive operations $\phi$ of
arity $n$ over those base types. The syntax is defined in \figref{syntax}. Types includes base types $\rho$
drawn from $\PrimTy$, along with standard type formers for sums, products, functions and lists, plus a type
constructor $\tyLift$ to allow approximation points to be added explicitly, as discussed in
\secref{models-of-total-gps}. Terms include variables, the usual introduction and elimination forms, a monadic
return and bind for lifted terms, and primitive operations $\phi$.

The language is intentionally minimal: it excludes general recursion, and general inductive or coinductive
types, which we will consider in future work (\secref{conclusion}). Typing judgments for terms are standard
and shown in \figref{typing}, with the usual rules for products, sums, functions, lists and lifting.

@@

\paragraph{Base types and operations}
A \emph{model} of a signature in a category $\cat{C}$ with finite products and a terminal object assigns to
each base type $\rho \in \PrimTy$ an object $\sem{\rho}_{\PrimTy}$ in $\cat{C}$ and to each primitive
operation $\phi \in \PrimOp^\rho_{\rho_1,\ldots,\rho_n}$ a morphism $\sem{\phi}_{\Op}: \sem{\rho_1}_{\PrimTy}
\times \ldots \times \sem{\rho_n}_{\PrimTy} \to \sem{\rho}_{\PrimTy}$.
